---
title: "Computational cognitive science - SDT"
author: "Filip Děchtěrenko"
date: "15 dubna 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

if(!require(pander)) {install.packages("pander")}

source("https://raw.githubusercontent.com/fidadoma/psychophysics_course_SDT/12d6db71cbe5dbda9e1d6bc8c4b19ee59ee6a1ff/utils.R")
```

## R Markdown

download data from https://figshare.com/articles/Mammogram_and_Face_Data/5248513. Data is from the article https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6092273/


```{r download data, message = F}
df <- read_csv("https://ndownloader.figshare.com/files/8973241")

df %>% head() 

```

Data are coded as follows:

* for mammograph stimuli
    * response = 0 - normal
    * response = 1 - abnormal
  
* for face stimuli
    * response = 0 - neutral expression
    * response = 1 - happy expression


# Selection of participant

Select just participant with username = 4

```{r select subject 4}

```

# Contingency tables

For each combination of stimuli type and orientation (2x2 outcomes), compute contingency tables with number of hits, FA, correct rejection and misses. You can use `xtabs()` or dplyr syntax. Hits and FA save as vector into variables  `Hs` and `FAs`. Values in vector should be in order mammographs-normal, mammograph-inverted, faces-normal, faces-inverted. 

```{r contingency tables}

```

# Senzitivity

Compute d' for individual conditions. You can use function `compute_dprime(H,FA)`. Funciton works in vector form, so you can use `compute_dprime(c(H1,H2),c(FA1,FA2))`, where H1/H2 and FA1/FA2 are hit rates and FA rate for both conditions.

```{r dprime}

```

# Bias

Compute c a c' for individual conditions. You can use function `compute_bias(H,FA, type = XX)`, where type is one of the options "C", "C_rel","lnB"

```{r bias}

```

# Visualization

Based on the analysis and following plot, explain the difference in performance.

```{r visualization}

df_plot <- tibble(H = Hs, FA = FAs, type1 = c("mammograph","mammograph","photography","photography"), type2 = c("normal","inverted","normal","inverted"))

df_plot %>% plot_normal_ROC_forDU()
```