---
title: "Computational cognitive science - intro statistics"
author: "Filip Děchtěrenko"
date: "15 dubna 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if(!require(tidyverse)) {install.packages("tidyverse")}
if(!require(pander)) {install.packages("pander")}
if(!require(ez)) {install.packages("ez")}

library(tidyverse)
library(ez)

source("https://raw.githubusercontent.com/fidadoma/psychophysics_course_SDT/12d6db71cbe5dbda9e1d6bc8c4b19ee59ee6a1ff/utils.R")
```

## R Markdown

download data from https://figshare.com/articles/Mammogram_and_Face_Data/5248513. Data is from the article https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6092273/


```{r download data, message = F}
df <- read_csv("https://ndownloader.figshare.com/files/8973241")

df %>% head() 

```

Data are coded as follows:

* for mammograph stimuli
    * response = 0 - normal
    * response = 1 - abnormal
  
* for face stimuli
    * response = 0 - neutral expression
    * response = 1 - happy expression

# Basic verbs

## Filter

Selects data based on some condition

```{r}
df %>% 
  filter(yearsExperience >3)

# we can use conbine it
df %>% 
  filter((actual_response==0 & correct_response == 1) | (actual_response==1 & correct_response == 0))

# or use string maniulations

df %>% 
  filter(stimType == "mammogram")

```

## Select

Selects only several columns

```{r}
df %>% 
  select(actual_response, correct_response)
# many helper functions
df %>% 
  select(ends_with("response"))

```

## Mutate

Creates new variable (for each row)

```{r}
df %>% 
  mutate(bare_stimName = basename(stimName))
```


## Group_by and summarise

Helpful combination, can get aggregates per each group. Group_by creates smaller subgroups, while summarize aggregates whole group by some functions

```{r}
df %>% 
  group_by(medicalSpecialty) %>% 
  summarize(mean_years = mean(yearsExperience),
            sd_years = sd(yearsExperience))
```

# visualization

we use library `ggplot2` which is bundled within tidyverse. We use `aes` to specify the aesthetics for the data.

```{r}
df %>% 
  ggplot(aes(x = medicalSpecialty, y = yearsExperience)) +
  stat_summary(fun.data  = "mean_cl_boot") + 
  theme(aspect.ratio = 1)

```

# your task

## Add whether response is correct

you can use `mutate` verb. Anser is correct, is actual and correct response are in sync

```{r}

```

## Test average accuracy between mammogram and faces

```{r}

```

## complex model - Test differences in accuracy between medical speciality, stimtype and orientation (3-way ANOVA)

```{r}
```



# Really complex model

Reason, why we use R for analysis :-)

This needs some Bayesian packages installed first

```{r}

library(brms)
df1 <- df %>% mutate(correct = as.numeric(actual_response == correct_response), yearsExperience = scale(yearsExperience))

df1 %>% 
  ggplot(aes(x = stimType, y =correct, color = orientation, group = orientation)) +
  stat_summary(fun.data  = "mean_cl_boot") + 
  stat_summary(fun = "mean", geom = "line") + 
  theme(aspect.ratio = 1)


brm1 <- brm(correct~stimType*orientation*medicalSpecialty+yearsExperience + (1|username)+(1|stimName),
            family = bernoulli(link = "probit"),
            data = df1,
            prior = c(
              prior(normal(0, 1), class = Intercept),
              prior(normal(0, 1), class = b) 
            ),iter = 2000, chains = 4, cores = 4,
  control = list(adapt_delta = 0.98),
  file = "brm_example", 
  seed = 1
)
summary(brm1)
```