---
title: "Psychometric curves"
author: "Filip Dechterenko"
date: "2 prosince 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(message = F)
```

```{r}

library(tidyverse) 
library(psych)
theme_set(theme_classic(16))
library(MPDiR)
```

We are using data from Hecht, Schlaer and Pirenne (1942)

```{r load data}
data(HSP) 
names(HSP) <- c("Quanta", "PerCent", "N", "Obs", "Run")
HSP <- HSP %>% 
  as_tibble() %>% 
  mutate(PerCent = PerCent/100)
```

## Visualize

We have three observers

```{r}
qplot(Quanta, PerCent,
      colour=Obs, size=I(5),
      data=HSP)
```

When plotted on logaritmic scale, they looked like a sigmoidal fit

```{r}
qplot(log(Quanta), PerCent,
      colour=Obs, size=I(5),
      data=HSP)
```

And for individual runs
```{r}
qplot(Quanta, PerCent,
      colour=Obs, size=I(5),
      data=HSP) + facet_grid(Run ~ Obs)
```

Now let's add number of yes and no responses
```{r}
HSP <- HSP %>% mutate(
  NumYes = round(N * PerCent),
  NumNo = N - NumYes)

head(HSP) %>% 
  knitr::kable()
```

Select sjsut one run and one observer and visualize it

````{r}
SHR1 <- HSP %>% filter(Obs=="SH", Run=="R1")

qplot(log(Quanta), NumYes,
      size=I(5),
      data=SHR1) + geom_point(aes(y=NumNo), shape=I(2), size=I(5), colour=I("red"))
```

We can manually fit psychometric curve using CDF as inner function

```{r}
SHR1.glm <- glm(formula = cbind(NumYes, NumNo) ~ log(Quanta),
                family = binomial(probit), data = SHR1)
summary(SHR1.glm)
anova(SHR1.glm, test = "Chisq")
coef(SHR1.glm)
confint(SHR1.glm)
```

And visualize the fit. First, just visualize the data

```{r}
pp <- qplot(Quanta, PerCent,
      size=I(5), 
      data=SHR1) + xlab("Quanta/Flash") + ylab("Proportion \"seen\"") + 
  ggtitle("Obs: SH, Run: 1") +
  scale_x_log10(breaks=c(25,50,100,200,400), limit=c(20,440))
pp
```

Add the curve and the band

```{r}
xseq <- seq(20,450, len=100)
SHR1.pred <- predict(SHR1.glm, newdata = data.frame(Quanta = xseq), 
                     type = "response", se.fit = T)
SHR1.pred <- data.frame(x=xseq, fit=SHR1.pred$fit, se.fit=SHR1.pred$se.fit)
head(SHR1.pred)
pp + geom_line(aes(x=x,y=fit), data=SHR1.pred)
pp + geom_ribbon(data=SHR1.pred, 
                 aes(x=x, ymin=fit-se.fit, ymax=fit+se.fit, y=fit), fill="gray")

pf <- pp + geom_ribbon(data=SHR1.pred, 
                 aes(x=x, ymin=fit-se.fit, ymax=fit+se.fit, y=fit), fill="gray") +
  geom_line(aes(x=x,y=fit), data=SHR1.pred) +
  geom_point(size=I(5), colour=I("black"))
pf
```

From estimated parameters, we can compute threshold

```{r}
q.5   <- -coef(SHR1.glm)[1] / coef(SHR1.glm)[2]
sigma <- 1/coef(SHR1.glm)[2]

thresh.est <- function(p.est, model) {
  q.5   <- -coef(model)[1] / coef(model)[2]
  sigma <- 1/coef(model)[2]
  th <- exp(qnorm(p = p.est,
                  mean = q.5, sd = sigma))
  return(th)
}
thresh.est(.6, SHR1.glm)

th.6 <- (thresh.est(.6,SHR1.glm))
pf + geom_hline(yintercept=0.6, linetype="dotted") + 
  geom_vline(xintercept=th.6, linetype="dotted")


```

Similar can be done within quickpsy

```{r}
library(quickpsy)

fit <- quickpsy(HSP, Quanta, PerCent, grouping = c("Obs", "Run")) 
plot(fit, color = Run)

fit$thresholds

quickpsy::thresholds(fit, 0.6)

```

